Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2019-06-30 manuscript_pretty.Rmd
begin revisions / add expo

keywords          : "Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance"
wordcount         : "4024 \\vspace{2mm} \\par \\textit{Public Significance Statement:} Contextual cues have been shown to automatically trigger adjustments in selective attention independent of awareness and intention. Here, we find the task-relevance plays an important role in determining which context cues are used to direct attention. These findings contribute to a better understanding of how context-dependency might occur in more complex environments and more generally, how learning and memory processes enable flexible control over attention."

@@

#output: 
#  word_document

@@

header-includes:
  - \usepackage{setspace}\doublespacing 
  - \newenvironment{zeroindent}
     {\par\setlength{\parindent}{0pt}}
     {\par}  
  - \setlength{\parskip}{0pt}
  - \raggedbottom

@@

source("data-analysis/analysis.R")
source("data-analysis/table1.R")
```

@@

One explanation for CSPC effects is that the repeated application of attentional priorities in a particular context creates an associative link in episodic memory between the attentional control procedures and the contextual information [@abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014]. Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating associated attentional priorities. As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion. However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.

@@

# The Current Study

@@

# Methods
```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
knitr::include_graphics("images/Task.jpg")
```

@@

```{r figure2, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
#print figure 2
#source: data-analysis/analysis.R
figure2
```

(ref:figure2) Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).

@@

```{r echo = FALSE, warning = FALSE, message=FALSE, results='asis'}
#print latex table
cat(TR_Table)
```

@@

\newpage

>>>>

keywords          : "Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance"
wordcount         : "4024 \\vspace{2mm} \\par \\textit{Public Significance Statement:} Contextual cues have been shown to automatically trigger adjustments in selective attention independent of awareness and intention. Here, we find that task-relevance plays an important role in determining which context cues are used to direct attention. These findings contribute to a better understanding of how context-dependency might occur in more complex environments and more generally, how learning and memory processes enable flexible control over attention."

@@

indent: TRUE
#output: 
#  word_document

@@

header-includes:
  - \usepackage{setspace}\singlespacing 
  # - \newenvironment{zeroindent}
  #    {\par\setlength{\parindent}{5pt}}
  #    {\par}  
  - \setlength{\parskip}{0pt}
  - \raggedbottom

@@

source("data-analysis/analysis_E1.R")
source("data-analysis/analysis_E2.R")
source("data-analysis/analysis_E3.R")
source("data-analysis/table1.R")
source("data-analysis/analysis_E1_Exploratory.R")
```

@@

One explanation for CSPC effects is that the repeated application of attentional priorities in a particular context creates an associative link in episodic memory between the attentional control procedures and the contextual information [@abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014]. Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating associated attentional priorities. As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion. How associations between attentional priorities and context cues are formed and used still remains unclear however. The current study addresses two issues.

First, how is attentional control resolved when multiple contextual features could be used as cues? Second, it remains unclear how  Historically, theories of automaticity and attentional control have emphasized the role of practice and likened the process to skill-learning ().

However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.

<!-- 
Furthermore, understanding how associations are formed and used is not well understood. Theories of automaticity and attentional control historically have emphasized the role of practice - difficult to suppress once learned.. Shiffrin and Schneider, Treisman, etc.. everyone basically.

Early CSPC work too thought that practice is important for "associations to form"

Memory-based theories on the other hand, take a more nuanced view. Practice is only important to the extent that improves memory retrieval. If retrieval cues can --  distinguish between prior episodes.

Therefore, the skill-learning view of automaticity would predict that associations take time to develop through practice, and once learned, difficult to suppress. 
-->

@@

# Experiment 1

@@

# Methods
```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
#, out.width="\\textwidth", fig.env="figure*"
knitr::include_graphics("images/Task.jpg")
```

@@

```{r figure2, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
#, out.width="\\textwidth", fig.env="figure*"
#print figure 2
#source: data-analysis/analysis.R
figure2
```

(ref:figure2) Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent). Task-relevance was manipulated by the secondary feature-counting task.

@@

## Exploratory Analyses: Order Effects

```{r figure2b, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
#, out.width="\\textwidth", fig.env="figure*"
#print figure 2
#source: data-analysis/analysis.R
figure2B
```

Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical. Abrahamse et al.... found that...  In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.

To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100% congruent to 0% congruent (100%-0%) or 0% congruent to 100% congruent (0%-100%). We again removed participants with error rates greater than 25% and adopted the same outlier removal procedure as described above. We submitted mean correct RTs for frequency unbiased items to a 2x2x2 mixed ANOVA with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and phase order (100%-0% and 0%-100%) as the between-subjects factor.

Consistent with the original analysis, two-way interaction between task-relevant context and congruency remained significant,`r E1_Order_A$Congruency_Task_Relevant_Context`. However, the three-way interaction was non-significant, `r E1_Order_A$Order_Congruency_Task_Relevant_Context`. Therefor, we did not find statistical support for a list-shift asymmetry. Additionally, the asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior results ().

We also conducted a more severe test of the list-shift hypothesis. Abrahamse et al.'s interpretation of the list shift effect was that participants had to learn to adjust to the new cues. Therefore, we might expect that any asymmetry would be exaggerated near the point of transition. We repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.

Again, the three-way interaction was non-significant, `r E1_Order_B$Order_Congruency_Task_Relevant_Context`. Interestingly, the two-way interaction between congruency and task-relevant context is also still significant, `r E1_Order_B$Congruency_Task_Relevant_Context`. This result supports the notion there was no asymmetry and that the shift in context-dependent effects occur almost immediately after the transition.

```{r echo=FALSE, results='asis'}
#, fig.align="center", fig.cap="" ,out.width="\\textwidth", fig.env="figure*"
cat(TR_Table)

#knitr::include_graphics("images/table1.pdf")
```

<!-- ```{r echo=FALSE, echo = FALSE, warning = FALSE, message=FALSE, results='asis', out.width="\\textwidth"} -->
<!-- #print latex table -->
<!-- cat(TR_Table) -->
<!-- ``` -->

# Experiment 2

In Experiment 1, we found that

# Methods

## Participants
All participants were recruited from Amazon Mechanical Turk (AMT) and compensated $2.00 for participating. The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by $6.00 per hour. For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study. Participants were included in the study if they completed all trials. We posted 50 HITs and 50 participants completed all trials.

The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.

## Design 
Experiment 1 used a 2x3 within-subjects design with proportion congruent (25%, 50%, and 75%) and  congruency (congruent and incongruent) as factors. The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations. The design in every other respect was identical to Experiment 1.

## Procedure
All participants were AMT workers who found the experiment using the AMT system. The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board. Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form. Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window. Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing 'z' if the arrow pointed left, and 'm' if the arrow pointed right.

```{r figure3, echo=FALSE, fig.width=3.6, fig.height=4, fig.cap='(ref:figure3)'}
#print figure 3
#source: data-analysis/analysis_E2.R
figure3
```

(ref:figure3) Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25%, 75%, and 100% PC) in reaction times (left) and error rates (right).

# Results
Participants with mean error rates greater than 25% were excluded from the analyses, eliminating `r N_subjects_removed_E2` participants. For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure. The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms [@van_selst_solution_1994]. This procedure removed `r round(percent_removed_E2*100,digits = 2)`% of the total observations.

The questions of interest were whether participants would learn the associations between the context cues without the task-relevance manipulation (i.e., the counting task) and whether responding to the unbiased cues would be influenced by the presence of the biased cues. To that end, mean correct RTs and mean error rates were submitted to an analysis of variance (ANOVA) with proportion congruent (25%, 50%, and 75%) and congruency (congruent and incongruent) as within-subject factors.

The results of the RT analysis revealed the critical, two-way interaction between proportion congruency and congruency to be non-significant, `r RT_ANOVA_E2$PC_Congruency`. Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA_E2$PC_Congruency`. Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effect.

# Experiment 3

# Methods

## Participants
All participants were recruited from Amazon Mechanical Turk (AMT) and compensated $2.00 for participating. The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by $6.00 per hour. For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study. Participants were included in the study if they completed all trials. We posted 50 HITs and 50 participants completed all trials.

The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.

## Design 
Experiment 1 used a 2x3 within-subjects design with proportion congruent (25%, 50%, and 75%) and  congruency (congruent and incongruent) as factors. The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations. The design in every other respect was identical to Experiment 1.

## Procedure
All participants were AMT workers who found the experiment using the AMT system. The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board. Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form. Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window. Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing 'z' if the arrow pointed left, and 'm' if the arrow pointed right.

```{r figure4, echo=FALSE, fig.cap='(ref:figure4)', fig.width=3.6, fig.height=3.5}
#print figure 3
#source: data-analysis/analysis_E2.R
figure4
```

(ref:figure4) Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent). Task-relevance was manipulated through explicit instructions.

# Results
Participants with mean error rates greater than 25% were excluded from the analyses, eliminating `r N_subjects_removed_E3` participants. For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure. The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms [@van_selst_solution_1994]. This procedure removed `r round(percent_removed_E3*100,digits = 2)`% of the total observations.

The primary question of interest was whether the task-relevance of context features (made relevant through explicit task instructions) associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items. Mean correct RTs and mean error rates from frequency unbiased trials were submitted to an analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors.

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, `r RT_ANOVA_E3$Task_Relevant_Context_Congruency`. Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA_E3$Task_Relevant_Context_Congruency`.

@@

### 2019-06-30 manuscript_pretty.tex
begin revisions / add expo

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
    \setmainfont[]{Times New Roman}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Contextual recruitment of selective attention can be updated via changes in task-relevance},
            pdfauthor={Nicholaus P. Brosowsky~\& Matthew J. C. Crump},
            pdfkeywords={Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
\usepackage{setspace}\doublespacing
\newenvironment{zeroindent} {\par\setlength{\parindent}{0pt}} {\par}
\setlength{\parskip}{0pt}
\raggedbottom

@@

\hypertarget{the-current-study}{%
\section{The Current Study}\label{the-current-study}}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).}
\end{figure}

@@

@@

>>>>

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
    \setmainfont[]{Times New Roman}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Contextual recruitment of selective attention can be updated via changes in task-relevance},
            pdfauthor={Nicholaus P. Brosowsky~\& Matthew J. C. Crump},
            pdfkeywords={Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
\usepackage{setspace}

\singlespacing
\setlength{\parskip}{0pt}
\raggedbottom

@@

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

@@

\begin{figure}
\centering
\includegraphics{manuscript_pretty_files/figure-latex/figure2-1.pdf}
\caption{\label{fig:figure2}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent). Task-relevance was manipulated by the secondary feature-counting task.}
\end{figure}

@@

\hypertarget{exploratory-analyses-order-effects}{%
\subsection{Exploratory Analyses: Order Effects}\label{exploratory-analyses-order-effects}}

\begin{figure}
\centering
\includegraphics{manuscript_pretty_files/figure-latex/figure2b-1.pdf}
\caption{\label{fig:figure2b}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent). Task-relevance was manipulated by the secondary feature-counting task.}
\end{figure}

Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical. Abrahamse et al\ldots{}. found that\ldots{} In our study, we were primarily interested in whether participants could use context cues despite the presence of competing, contradictory cues, and whether they could switch from one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.

To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100\% congruent to 0\% congruent (100\%-0\%) or 0\% congruent to 100\% congruent (0\%-100\%). We again removed participants with error rates greater than 25\% and adopted the same outlier removal procedure as described above. We submitted mean correct RTs for frequency unbiased items to a 2x2x2 mixed ANOVA with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and phase order (100\%-0\% and 0\%-100\%) as the between-subjects factor.

Consistent with the original analysis, two-way interaction between task-relevant context and congruency remained significant,\(F(1, 129) = 8.92\), \(\mathit{MSE} = 1,627.84\), \(p = .003\), \(\hat{\eta}^2_p = .065\). However, the three-way interaction was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 1,627.84\), \(p = .112\), \(\hat{\eta}^2_p = .019\). Therefor, we did not find statistical support for a list-shift asymmetry. Additionally, the asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior results ().

We also conducted a more severe test of the list-shift hypothesis. Abrahamse et al.'s interpretation of the list shift effect was that participants had to learn to adjust to the new cues. Therefore, we might expect that any asymmetry would be exaggerated near the point of transition. We repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.

Again, the three-way interaction was non-significant, \(F(1, 129) = 0.02\), \(\mathit{MSE} = 2,866.15\), \(p = .902\), \(\hat{\eta}^2_p = .000\). Interestingly, the two-way interaction between congruency and task-relevant context is also still significant, \(F(1, 129) = 6.65\), \(\mathit{MSE} = 2,866.15\), \(p = .011\), \(\hat{\eta}^2_p = .049\). This result supports the notion there was no asymmetry and that the shift in context-dependent effects occur almost immediately after the transition.

@@

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

In Experiment 1, we found that

\hypertarget{methods-1}{%
\section{Methods}\label{methods-1}}

\hypertarget{participants-1}{%
\subsection{Participants}\label{participants-1}}

All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating. The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour. For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study. Participants were included in the study if they completed all trials. We posted 50 HITs and 50 participants completed all trials.

\hypertarget{apparatus-stimuli-1}{%
\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli-1}}

The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.

\hypertarget{design-1}{%
\subsection{Design}\label{design-1}}

Experiment 1 used a 2x3 within-subjects design with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as factors. The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations. The design in every other respect was identical to Experiment 1.

\hypertarget{procedure-1}{%
\subsection{Procedure}\label{procedure-1}}

All participants were AMT workers who found the experiment using the AMT system. The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board. Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form. Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window. Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing \enquote{z} if the arrow pointed left, and \enquote{m} if the arrow pointed right.

\begin{figure}
\centering
\includegraphics{manuscript_pretty_files/figure-latex/figure3-1.pdf}
\caption{\label{fig:figure3}Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25\%, 75\%, and 100\% PC) in reaction times (left) and error rates (right).}
\end{figure}

\hypertarget{results-1}{%
\section{Results}\label{results-1}}

Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 3 participants. For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure. The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994). This procedure removed 3.14\% of the total observations.

The questions of interest were whether participants would learn the associations between the context cues without the task-relevance manipulation (i.e., the counting task) and whether responding to the unbiased cues would be influenced by the presence of the biased cues. To that end, mean correct RTs and mean error rates were submitted to an analysis of variance (ANOVA) with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as within-subject factors.

The results of the RT analysis revealed the critical, two-way interaction between proportion congruency and congruency to be non-significant, \(F(2, 92) = 0.85\), \(\mathit{MSE} = 498.56\), \(p = .431\), \(\hat{\eta}^2_p = .018\). Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(2, 92) = 0.45\), \(\mathit{MSE} = 4.61\), \(p = .641\), \(\hat{\eta}^2_p = .010\). Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effect.

\hypertarget{experiment-3}{%
\section{Experiment 3}\label{experiment-3}}

\hypertarget{methods-2}{%
\section{Methods}\label{methods-2}}

\hypertarget{participants-2}{%
\subsection{Participants}\label{participants-2}}

All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating. The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour. For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study. Participants were included in the study if they completed all trials. We posted 50 HITs and 50 participants completed all trials.

\hypertarget{apparatus-stimuli-2}{%
\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli-2}}

The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.

\hypertarget{design-2}{%
\subsection{Design}\label{design-2}}

Experiment 1 used a 2x3 within-subjects design with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as factors. The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations. The design in every other respect was identical to Experiment 1.

\hypertarget{procedure-2}{%
\subsection{Procedure}\label{procedure-2}}

All participants were AMT workers who found the experiment using the AMT system. The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board. Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form. Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window. Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing \enquote{z} if the arrow pointed left, and \enquote{m} if the arrow pointed right.

\begin{figure}
\centering
\includegraphics{manuscript_pretty_files/figure-latex/figure4-1.pdf}
\caption{\label{fig:figure4}Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent). Task-relevance was manipulated through explicit instructions.}
\end{figure}

\hypertarget{results-2}{%
\section{Results}\label{results-2}}

Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 4 participants. For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure. The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994). This procedure removed 3.42\% of the total observations.

The primary question of interest was whether the task-relevance of context features (made relevant through explicit task instructions) associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items. Mean correct RTs and mean error rates from frequency unbiased trials were submitted to an analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors.

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, \(F(1, 45) = 0.02\), \(\mathit{MSE} = 2,015.27\), \(p = .876\), \(\hat{\eta}^2_p = .001\). Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 45) = 0.66\), \(\mathit{MSE} = 14.26\), \(p = .420\), \(\hat{\eta}^2_p = .014\).
